Parallel forecasting

### 2020-12-08 r_notebooks/parallel_forecasting.Rmd
parallised prophetModels()

```{r, setup}
# Packages ####
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(fasster)
library(furrr)
library(knitr)

@@

## Read from local file
gp <- read_rds("../data/gp_linked_na_omit.rds")
oc <- read_rds("../data/oral_contraceptives.rds")

## Sort into monthly count data

oc_monthly_quantity_gp <- 
  countRegional(oc, PracticeID, datename, Quantity) %>% 
  right_join(gp, by = c("regional_unit" = "PracticeID")) %>% # want to have GPs which have recorded data for the duration, not just part of it as that would add noise
  mutate(n = 1000*n/npat) # quantity per 1000 pts

## Sort into monthly count data pre-lockdown (2020-03-23)

@@

## Smaller GP data set to develop process
regions <- unique(as.character(gp$PracticeID))
dev_data <- 
  oc_monthly_quantity_gp_pre_cv19 %>% 
  filter(regional_unit %in% sample(regions, 5))

@@

##### multisession
```{r, eval=FALSE}
plan(multisession)

system.time(proph_fit2 <- map_dfr(.x = unique(dev_data$regional_unit), 
             .f = ~regionalProphetFits(dev_data, .x)))

@@

>>>>

```{r, setup}
# Packages ####
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)
library(knitr)

@@

## Read from local file
#gp <- read_rds("../data/gp_linked_na_omit.rds")
gp <- read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL) %>% 
  filter(year == 2020) # do something better
oc <- read_rds("../data/oral_contraceptives.rds")

## Sort into monthly count data
oc_monthly_count <- oc %>% 
  group_by(datename) %>% 
  summarise(n = sum(Quantity)) %>% 
  mutate(datename = yearmonth(datename),
         n = case_when(str_detect(datename, pattern = "Jan") ~ n/31,
                       str_detect(datename, pattern = "Feb") ~ n/28.25,
                       str_detect(datename, pattern = "Mar") ~ n/31,
                       str_detect(datename, pattern = "Apr") ~ n/30,
                       str_detect(datename, pattern = "May") ~ n/31,
                       str_detect(datename, pattern = "Jun") ~ n/30,
                       str_detect(datename, pattern = "Jul") ~ n/31,
                       str_detect(datename, pattern = "Aug") ~ n/31,
                       str_detect(datename, pattern = "Sep") ~ n/30,
                       str_detect(datename, pattern = "Oct") ~ n/31,
                       str_detect(datename, pattern = "Nov") ~ n/30,
                       str_detect(datename, pattern = "Dec") ~ n/31)) %>% 
  ungroup() %>% 
  as_tsibble(index = datename)
colnames(gp)

oc_monthly_quantity_hb <- 
  right_join(oc, select(gp, c(practiceid, hboard)), 
             by = c("PracticeID" = "practiceid")) %>%
  countRegional(hboard, datename, Quantity) %>% 
  left_join(gp %>% 
  select(c(practiceid, npat, hboard)) %>% 
  group_by(hboard) %>% 
  summarise(npat = sum(npat)), by = c("regional_unit" = "hboard")) %>% 
  mutate(n = 1000*n/npat) # quantity per 1000 pts

oc_monthly_quantity_cluster <- 
  right_join(oc, select(gp, c(practiceid, cluster)), 
             by = c("PracticeID" = "practiceid")) %>%
  countRegional(cluster, datename, Quantity) %>% 
  left_join(gp %>% 
  select(c(practiceid, npat, cluster)) %>% 
  group_by(cluster) %>% 
  summarise(npat = sum(npat)), by = c("regional_unit" = "cluster")) %>% 
  mutate(n = 1000*n/npat) # quantity per 1000 pts

oc_monthly_quantity_gp <- 
  countRegional(oc, PracticeID, datename, Quantity) %>% 
  right_join(select(gp, c(practiceid, npat)), 
            by = c("regional_unit" = "practiceid")) %>% 
  mutate(n = 1000*n/npat)

## Sort into monthly count data pre-lockdown (2020-03-23)
oc_monthly_count_pre_cv19 <- 
  oc_monthly_count %>% 
  filter(datename < dmy("01-03-2020"))

oc_monthly_quantity_hb_pre_cv19 <- 
  oc_monthly_quantity_hb %>% 
    filter(datename < dmy("01-03-2020"))

oc_monthly_quantity_cluster_pre_cv19 <- 
  oc_monthly_quantity_cluster %>% 
    filter(datename < dmy("01-03-2020"))

@@

## Smaller GP data set to develop process
regions <- unique(as.character(gp$practiceid))
dev_data <- 
  oc_monthly_quantity_gp_pre_cv19 %>% 
  filter(regional_unit %in% sample(regions, 5))

@@

### future_map()

##### multisession

```{r, eval=FALSE}
plan(multisession)

system.time(proph_fit2 <- future_map_dfr(.x = unique(dev_data$regional_unit), 
             .f = ~regionalProphetFits(dev_data, .x),
            .options = furrr_options(seed = TRUE)))

@@

* 2020-12-07 Fails:

```
1 error encountered for oc_prophet_model1
[1] unable to load shared object '/Library/Frameworks/R.framework/Versions/4.0/Resources/library/prophet/libs/prophet.so':
  dlopen(/Library/Frameworks/R.framework/Versions/4.0/Resources/library/prophet/libs/prophet.so, 6): Library not loaded: @rpath/libtbb.dylib
  Referenced from: /Library/Frameworks/R.framework/Versions/4.0/Resources/library/prophet/libs/prophet.so
  Reason: image not found
```

* 2020-12-08 Fixed
  * Reinstalling using `install.packages("prophet", type="source")` has resolved problem.
  * Need to test in Windows
